Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-12 paper/paper.results.tex
Clean up table & wording in results section

In order to evaluate the generated schedule and compare it with the manually created schedule, we outline the adherence of each schedule to the constraints presented in table \ref{tbl:constraint-summary}. As we can see from table \ref{tbl:constraints-comparison}, the generated schedule was able to satisfy all mandatory constraints, however for the years of [???] it could not find an optimal schedule while ensuring that the block assignments are spread out ([???] constraint). On the other hand, we can see that the manually created schedule was not able to satisfy all mandatory constraints. In particular, we see that it contains consecutive block assignments for the years of [???], [...]. Evaluating the objectives, we see that [...\textit{request conflicts}]. Moreover, the manual schedule does not attempt to align weekend assignments with block assignments, unlike the optimal schedule found by the software.

>>>>

In order to evaluate the generated schedule and compare it with the manually created schedule, we outline the adherence of each schedule to the constraints presented in table \ref{tbl:constraint-summary}. As we can see from table \ref{tbl:constraints-comparison}, the optimal schedule generated using the software was able to satisfy all mandatory constraints. On the other hand, we can see that the manually created schedule was not able to satisfy all mandatory constraints. In particular, we see that it assigned clinicians to multiple consecutive blocks for all four years. Moreover, the manual schedule did not have an equal distribution of weekends and holidays for all four years of data. Evaluating the objectives, we see that [...\textit{request conflicts}]. Moreover, the manual schedule does not attempt to align weekend assignments adjacent to block assignments.
